%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%

\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
% Header
\begin{center}
    {\Huge\textbf{PU JIAO}}\\[0.5em]
    \small{
    \href{mailto:jiaopujp@gmail.com}{jiaopujp@gmail.com} | 
    \href{https://jpcoding.github.io/}{jpcoding.github.io}
    }\\[0.3em]
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/pu-jiao-4b309b212/}{Pu Jiao} | 
    \socialicon{\faGithub} \href{https://github.com/jpcoding}{jpcoding}
    }\\[0.2em]
    \small{Lexington, KY, United States}
\end{center}

\vspace{-4mm}


\section{\textbf{Research Interests}}
\vspace{-0.4mm}
\small{
High-Performance Computing 
Scientific Data Management, Analysis, and Reduction 
Deep Learning in High-Performance Computing and Data Compression
}
\vspace{-2mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{University of Kentucky}{Lexington, KY}
{Ph.D. in Computer Science}{Expected May 2026}

\resumeSubheading
{Missouri University of Science and Technology}{Rolla, MO}
{M.S. in Civil Engineering}{}

\resumeSubheading
{Institute of Engineering Mechanics, China Earthquake Administration}{Harbin, China}
{M.Eng. in Structural Engineering}{}

\resumeSubheading
{Xi'an Jiaotong University}{Xi'an, China}
{B.Eng. in Civil Engineering}{}

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {University of Kentucky}{Lexington, KY}
      {}{}
      \vspace{-3mm}
      %{\textbf{Research Assistant \& Teaching Assistant}}{August 2022 - Present}
      \resumeItemListStart
        \item Research Assistant, Computer Science Department (August 2022 - December 2024)
        \item Teaching Assistant, Computer Science Department (January 2025 - Present)
        \begin{itemize}[leftmargin=1em]
            \item[\textendash] CS216: Intro to Software Engineering Techniques; received "Excellent" ratings and 4.1-4.4/5 student evaluations
        \end{itemize}
      \resumeItemListEnd 
      % Detailed description for industry resumes:
      % Research Assistant:
      % \item Led research on artifact characterization and mitigation for error-controlled lossy compression, resulting in publications at VLDB, IPDPS, and ICDE
      % \item Developed novel adaptive quantization algorithms and quantity-of-interest preservation frameworks for scientific data compression
      % \item Collaborated with Argonne National Laboratory and multi-institutional teams on high-performance computing and compression optimization
      % Teaching Assistant:
      % \item Led in-person lab sessions for sections 002 \& 005, guided students through programming assignments, and held regular office hours
      % \item Graded assignments promptly and participated in TA meetings, providing feedback to instructor Dr. Pike
      % \item \textbf{Performance:} Received "Excellent" ratings across all categories; achieved 4.1-4.4/5 student ratings for clarity and debugging assistance 
  \resumeSubheading
    {Missouri University of Science and Technology}{}
    {}{}
    \vspace{-3mm}
    \resumeItemListStart
    \item Research Assistant, Computer Science Department (January 2022 - July 2022)
    \item Research Assistant, Civil Engineering Department (September 2019 - December 2021)
    \resumeItemListEnd



      % \item[\textbf{•}] \textbf{Computer Science Department (January 2022 - July 2022):}
    %   \item Developed Quantity of Interest (QoI) compression algorithms based on SZ3 compressor framework
    %   \item Implemented performance evaluation metrics and benchmarking tools for lossy compression analysis
    %   \item Collaborated with interdisciplinary team to optimize compression algorithms for scientific datasets
      % \item[\textbf{•}] \textbf{Civil Engineering Department (September 2019 - December 2021):}
    %   \item Used Computational Fluid Dynamics (CFD) to understand UAV ceiling effect under bridge decks, utilizing HandyScan 3D laser scanning for propeller modeling
    %   \item Participated in bridge inspection and data preprocessing using Flyability Elios, Skydio, Parrot Anifa, and FLIR thermal camera
    %   \item Collected earthquake records from PEER database, designed OpenSees models, and implemented parallel OpenSees instances using MATLAB
    % \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-6mm}

% \section{\textbf{Slected Publications} \hfill \textcolor{darkblue}{\scriptsize C=Conference, J=Journal, P=Patent, S=In Submission, T=Thesis}}
\section{\textbf{Selected Publications}}
\vspace{0.2mm}

\textbf{First-Author and Co-First-Author Publications:}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em]
\item Liu, Jinyang*, \textbf{Jiao, Pu*}, Zhao, Kai, Liang, Xin, Di, Sheng, Cappello, Franck (2025). \textbf{QPET: A Versatile and Portable Quantity-of-Interest-Preservation Framework for Error-Bounded Lossy Compression}. \textit{Proceedings of the VLDB Endowment}, Vol. 18. 2025. (To appear) (*Equal contribution)

\item \textbf{Jiao, Pu}, Di, Sheng, Xia, Mingze, Wu, Xuan, Liu, Jinyang, Liang, Xin, Cappello, Franck (2025). \textbf{Improving the Efficiency of Interpolation-Based Scientific Data Compressors with Adaptive Quantization Index Prediction}. In \textit{2025 IEEE International Parallel and Distributed Processing Symposium (IPDPS)}. IEEE. 2025. (To appear)

\item \textbf{Jiao, Pu}, Di, Sheng, Liu, Jinyang, Liang, Xin, Cappello, Franck (2023). \href{https://doi.org/10.1109/HiPC58850.2023.00027}{\textbf{Characterization and Detection of Artifacts for Error-Controlled Lossy Compressors}}. In \textit{2023 IEEE 30th International Conference on High Performance Computing, Data, and Analytics (HiPC)}, pp. 117-126. IEEE. December 2023, Goa, India. DOI: 10.1109/HiPC58850.2023.00027

\item \textbf{Jiao, Pu}, Di, Sheng, Guo, Hanqi, Zhao, Kai, Tian, Jiannan, Tao, Dingwen, Liang, Xin, Cappello, Franck (2022). \href{https://doi.org/10.14778/3574245.3574264}{\textbf{Toward Quantity-of-Interest Preserving Lossy Compression for Scientific Data}}. \textit{Proceedings of the VLDB Endowment}, Vol. 16, Issue 4, pp. 697-710. DOI: 10.14778/3574245.3574264
\end{enumerate}
}

\textbf{Co-Author Publications:}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em, resume]
\item Wu, Xuan, Di, Sheng, Ren, Congrong, \textbf{Jiao, Pu}, Xia, Mingze, Wang, Cheng, Guo, Hanqi, Liang, Xin, Cappello, Franck (2025). \textbf{Enabling Efficient Error-controlled Lossy Compression for Unstructured Scientific Data}. In \textit{2025 IEEE International Parallel and Distributed Processing Symposium (IPDPS)}. IEEE. 2025. (To appear)

\item Xia, Mingze, Wang, Bei, Li, Yuxiao, \textbf{Jiao, Pu}, Liang, Xin, Guo, Hanqi (2025). \href{https://doi.ieeecomputersociety.org/10.1109/ICDE65448.2025.00275}{\textbf{TspSZ: An Efficient Parallel Error-Bounded Lossy Compressor for Topological Skeleton Preservation}}. In \textit{2025 IEEE 41st International Conference on Data Engineering (ICDE)}, pp. 3682-3695. IEEE. May 2025. DOI: 10.1109/ICDE65448.2025.00275

\item Xia, Mingze, Di, Sheng, Cappello, Franck, \textbf{Jiao, Pu}, Zhao, Kai, Liu, Jinyang, Wu, Xuan, Liang, Xin, Guo, Hanqi (2024). \href{https://doi.org/10.1109/ICDE60146.2024.00378}{\textbf{Preserving Topological Feature with Sign-of-Determinant Predicates in Lossy Compression: A Case Study of Vector Field Critical Points}}. In \textit{2024 IEEE 40th International Conference on Data Engineering (ICDE)}, pp. 4979-4992. IEEE. May 2024. DOI: 10.1109/ICDE60146.2024.00378

\item Ma, Pengfei, Li, Jiaoli, Zhuo, Ying, \textbf{Jiao, Pu}, Chen, Genda (2023). \href{https://doi.org/10.3390/coatings13061008}{\textbf{Coating Condition Detection and Assessment on the Steel Girder of a Bridge through Hyperspectral Imaging}}. \textit{Coatings}, Vol. 13, Issue 6, pp. 1008. DOI: 10.3390/coatings13061008

\item Yuan, Xinzhe, Chen, Genda, \textbf{Jiao, Pu}, Li, Liujun, Han, Jun, Zhang, Haibin (2022). \href{https://doi.org/10.1016/j.engstruct.2022.113918}{\textbf{A neural network-based multivariate seismic classifier for simultaneous post-earthquake fragility estimation and damage classification}}. \textit{Engineering Structures}, Vol. 255, pp. 113918. DOI: 10.1016/j.engstruct.2022.113918

\item Yuan, Xinzhe, Tanksley, Dustin, \textbf{Jiao, Pu}, Li, Liujun, Chen, Genda, Wunsch, Donald (2021). \href{https://doi.org/10.3389/fbuil.2021.660103}{\textbf{Encoding time-series ground motions as images for convolutional neural networks-based seismic damage evaluation}}. \textit{Frontiers in Built Environment}, Vol. 7, pp. 660103. DOI: 10.3389/fbuil.2021.660103
\end{enumerate}
}

\section{\textbf{Service}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Reviewer:}
    {IEEE Transactions on Parallel and Distributed Systems (TPDS)}
  \resumeSubItem{Conference Volunteer:}
    {Student Volunteer, SC25 (The International Conference for High Performance Computing, Networking, Storage, and Analysis)}
 \resumeHeadingSkillEnd

\section{\textbf{Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {C++, Python, JavaScript, SQL, R, MATLAB}
  \resumeSubItem{High-Performance Computing:}
    {MPI, OpenMP, CUDA, parallel algorithms, scientific computing}
  \resumeSubItem{Build Systems \& Tools:}
    {CMake, Spack, Git, Linux/Unix systems}
  \resumeSubItem{Data Science \& Analysis:}
    {NumPy, Pandas, SciPy, Matplotlib, scikit-learn}
\resumeSubItem{Databases:}
    {MongoDB, MySQL, SQLite}
  \resumeSubItem{Compression Technologies:}
    {SZ2.1, SZ3, SZx, FPZIP, ZFP, lossy compression algorithms}
  \resumeSubItem{Simulation Software:}
    {OpenSees, CFD, ANSYS, structural analysis tools}
  \resumeSubItem{Research Methodologies:}
    {Algorithm design, performance optimization, artifact detection, experimental validation}
 \resumeHeadingSkillEnd


\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:} English (Fluent), Chinese (Native)

\textbf{Interests:} High-performance computing, scientific data compression, UAV technology, structural engineering
}
\vspace{-4mm}

\end{document}
