%
% Industry CV LaTeX Template (based on academic CV)
% Author: Pu Jiao
% Customized for Industry Applications
%

\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{\footnotesize{#4}}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubheadingContinue}[2]{
\vspace{0.5mm}
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textit{#1} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{PU JIAO}}\\[0.5em]
    \small{
    \href{mailto:jiaopujp@gmail.com}{jiaopujp@gmail.com} | 
    \href{https://jpcoding.github.io/}{jpcoding.github.io}
    }\\[0.3em]
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/pu-jiao-4b309b212/}{ } | 
    \socialicon{\faGithub} \href{https://github.com/jpcoding}{jpcoding}
    }\\[0.2em]
    \small{Lexington, KY, United States}
\end{center}

\vspace{-4mm}

\section{\textbf{Professional Summary}}
\vspace{-0.4mm}
\small{
PhD candidate in Computer Science with 5+ years of research experience in high-performance computing, data compression algorithms, and large-scale system optimization. Seeking opportunities in academia and industry to apply my expertise in developing efficient solutions that improve data processing efficiency. Proficient in C++, Python, and parallel computing frameworks with hands-on experience in cloud infrastructure and database management. Published researcher with 10+ peer-reviewed publications in top-tier venues.
}
\vspace{-2mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{University of Kentucky}{Lexington, KY}
{Ph.D. in Computer Science (Expected)}{May 2026}

\resumeSubheading
{Missouri University of Science and Technology}{Rolla, MO}
{M.S. in Civil Engineering}{}

\resumeSubheading
{Xi'an Jiaotong University}{Xi'an, China}
{B.Eng. in Civil Engineering}{}

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Technical Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {C++ (Advanced), Python (Advanced), JavaScript, SQL, R, MATLAB}
  \resumeSubItem{Frameworks \& Libraries:}
    {MPI, OpenMP, CUDA, NumPy, Pandas, SciPy, scikit-learn, TensorFlow}
  \resumeSubItem{Cloud \& Infrastructure:}
    {AWS, Docker, Kubernetes, Linux/Unix systems, Git, CI/CD pipelines}
  \resumeSubItem{Databases \& Storage:}
    {MongoDB, MySQL, SQLite, Redis, distributed storage systems}
  \resumeSubItem{Tools \& Technologies:}
    {CMake, Spack, REST APIs, microservices, data compression algorithms}
  \resumeSubItem{Specializations:}
    {High-performance computing, algorithm optimization, data analytics, machine learning}
 \resumeHeadingSkillEnd

\section{\textbf{Professional Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {University of Kentucky}{Lexington, KY}
      {Research Assistant}{Aug 2022 - Dec 2024}
      \resumeItemListStart
        \item Developed and implemented artifact detection algorithms for scientific lossy compression systems, focusing on characterization and mitigation strategies for data decompression artifacts
        \item Optimized interpolation-based compression algorithms through adaptive quantization techniques, achieving up to 90\% improvement in compression ratio while maintaining data quality
        \item Conducted comprehensive performance analysis of multiple lossy compressors (SZ2.1, SZ3, SZx, FPZIP, ZFP) for large-scale scientific datasets, establishing benchmarking standards
        \item Designed and implemented detection methodologies for posterization, interpolation, and tiling artifacts in compressed scientific data using advanced signal processing techniques
        \item Developed Python API interfaces for C++ compression libraries to enhance workflow efficiency and enable broader research community adoption
        \item Collaborated with Argonne National Laboratory research teams on high-performance computing optimization projects and compression algorithm development
      \resumeItemListEnd
      
      \resumeSubheadingContinue
      {Teaching Assistant}{Jan 2025 - Present}
      \resumeItemListStart
        \item CS216: Introduction to Software Engineering Techniques - led lab sessions and provided student support
        \item Received "Excellent" ratings across all teaching categories with 4.1-4.4/5 student evaluations
        \item Guided students through programming assignments and held regular office hours for debugging assistance
      \resumeItemListEnd
      
  \resumeSubheading
    {Missouri University of Science and Technology}{Rolla, MO}
    {Research Assistant @ Computer Science}{Jan 2022 - Jul 2022}
    \resumeItemListStart
    \item Developed Quantity of Interest (QoI) compression algorithms based on SZ3 compressor framework and conducted performance evaluations
    \item Implemented benchmarking tools for lossy compression analysis using C++ and Python
    \resumeItemListEnd
    
    \resumeSubheadingContinue
    {Research Assistant @ Civil Engineering}{Sep 2019 - Dec 2021}
    \resumeItemListStart
    \item Used Computational Fluid Dynamics (CFD) to understand UAV ceiling effects under bridge decks, utilizing HandyScan 3D laser scanning and reverse engineering software to build propeller models for CFD simulation
    \item Participated in bridge inspection and data preprocessing work using Flyability Elios, Skydio, Parrot Anafi, and FLIR thermal cameras
    \item Collected earthquake records from PEER database, designed OpenSees models, and implemented parallel running of OpenSees instances using MATLAB
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Publications}}
\vspace{-0.4mm}

\textbf{First-Author and Co-First-Author Publications:}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em]
\item \textbf{[VLDB'25]} Liu, Jinyang*, \textbf{Jiao, Pu*}, Zhao, Kai, Liang, Xin, Di, Sheng, Cappello, Franck (2025). \textbf{QPET: A Versatile and Portable Quantity-of-Interest-Preservation Framework for Error-Bounded Lossy Compression}. \textit{Proceedings of the VLDB Endowment}, Vol. 18. 2025. (To appear) (*Equal contribution)

\item \textbf{[IPDPS'25]} \textbf{Jiao, Pu}, Di, Sheng, Xia, Mingze, Wu, Xuan, Liu, Jinyang, Liang, Xin, Cappello, Franck (2025). \textbf{Improving the Efficiency of Interpolation-Based Scientific Data Compressors with Adaptive Quantization Index Prediction}. In \textit{2025 IEEE International Parallel and Distributed Processing Symposium (IPDPS)}. IEEE. 2025. (To appear)

\item \textbf{[HiPC'23]} \textbf{Jiao, Pu}, Di, Sheng, Liu, Jinyang, Liang, Xin, Cappello, Franck (2023). \href{https://doi.org/10.1109/HiPC58850.2023.00027}{\textbf{Characterization and Detection of Artifacts for Error-Controlled Lossy Compressors}}. In \textit{2023 IEEE 30th International Conference on High Performance Computing, Data, and Analytics (HiPC)}, pp. 117-126. IEEE. December 2023, Goa, India. DOI: 10.1109/HiPC58850.2023.00027

\item \textbf{[VLDB'22]} \textbf{Jiao, Pu}, Di, Sheng, Guo, Hanqi, Zhao, Kai, Tian, Jiannan, Tao, Dingwen, Liang, Xin, Cappello, Franck (2022). \href{https://doi.org/10.14778/3574245.3574264}{\textbf{Toward Quantity-of-Interest Preserving Lossy Compression for Scientific Data}}. \textit{Proceedings of the VLDB Endowment}, Vol. 16, Issue 4, pp. 697-710. DOI: 10.14778/3574245.3574264
\end{enumerate}
}

\textbf{Co-Author Publications:}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em, resume]
\item \textbf{[IPDPS'25]} Wu, Xuan, Di, Sheng, Ren, Congrong, \textbf{Jiao, Pu}, Xia, Mingze, Wang, Cheng, Guo, Hanqi, Liang, Xin, Cappello, Franck (2025). \textbf{Enabling Efficient Error-controlled Lossy Compression for Unstructured Scientific Data}. In \textit{2025 IEEE International Parallel and Distributed Processing Symposium (IPDPS)}. IEEE. 2025. (Best Paper)

\item \textbf{[ICDE'25]} Xia, Mingze, Wang, Bei, Li, Yuxiao, \textbf{Jiao, Pu}, Liang, Xin, Guo, Hanqi (2025). \href{https://doi.ieeecomputersociety.org/10.1109/ICDE65448.2025.00275}{\textbf{TspSZ: An Efficient Parallel Error-Bounded Lossy Compressor for Topological Skeleton Preservation}}. In \textit{2025 IEEE 41st International Conference on Data Engineering (ICDE)}, pp. 3682-3695. IEEE. May 2025. DOI: 10.1109/ICDE65448.2025.00275

\item \textbf{[ICDE'24]} Xia, Mingze, Di, Sheng, Cappello, Franck, \textbf{Jiao, Pu}, Zhao, Kai, Liu, Jinyang, Wu, Xuan, Liang, Xin, Guo, Hanqi (2024). \href{https://doi.org/10.1109/ICDE60146.2024.00378}{\textbf{Preserving Topological Feature with Sign-of-Determinant Predicates in Lossy Compression: A Case Study of Vector Field Critical Points}}. In \textit{2024 IEEE 40th International Conference on Data Engineering (ICDE)}, pp. 4979-4992. IEEE. May 2024. DOI: 10.1109/ICDE60146.2024.00378

\item Ma, Pengfei, Li, Jiaoli, Zhuo, Ying, \textbf{Jiao, Pu}, Chen, Genda (2023). \href{https://doi.org/10.3390/coatings13061008}{\textbf{Coating Condition Detection and Assessment on the Steel Girder of a Bridge through Hyperspectral Imaging}}. \textit{Coatings}, Vol. 13, Issue 6, pp. 1008. DOI: 10.3390/coatings13061008

\item Yuan, Xinzhe, Chen, Genda, \textbf{Jiao, Pu}, Li, Liujun, Han, Jun, Zhang, Haibin (2022). \href{https://doi.org/10.1016/j.engstruct.2022.113918}{\textbf{A neural network-based multivariate seismic classifier for simultaneous post-earthquake fragility estimation and damage classification}}. \textit{Engineering Structures}, Vol. 255, pp. 113918. DOI: 10.1016/j.engstruct.2022.113918

\item  Yuan, Xinzhe, Tanksley, Dustin, \textbf{Jiao, Pu}, Li, Liujun, Chen, Genda, Wunsch, Donald (2021). \href{https://doi.org/10.3389/fbuil.2021.660103}{\textbf{Encoding time-series ground motions as images for convolutional neural networks-based seismic damage evaluation}}. \textit{Frontiers in Built Environment}, Vol. 7, pp. 660103. DOI: 10.3389/fbuil.2021.660103
\end{enumerate}
}
\vspace{-2mm}

\section{\textbf{Service}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Reviewer:}
    {IEEE Transactions on Parallel and Distributed Systems (TPDS)}
  \resumeSubItem{Conference Volunteer:}
    {Student Volunteer, SC25 (The International Conference for High Performance Computing, Networking, Storage, and Analysis)}
 \resumeHeadingSkillEnd

\vspace{-2mm}

% \section{\textbf{Certifications \& Awards}}
% \vspace{-0.4mm}
% \small{
% \textbf{Professional Certifications:}
% \begin{itemize}[leftmargin=*, labelsep=0.5em]
% \item AWS Certified Solutions Architect (In Progress)
% \item Google Cloud Professional Data Engineer (In Progress)
% \end{itemize}

% \textbf{Awards \& Recognition:}
% \begin{itemize}[leftmargin=*, labelsep=0.5em]
% \item Outstanding Teaching Assistant Award, University of Kentucky (2025)
% \item Best Paper Finalist, IEEE HiPC Conference (2023)
% \item Graduate Research Fellowship, University of Kentucky (2022-2026)
% \end{itemize}
% }
% \vspace{-4mm}

\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:} English (Fluent), Chinese (Native)

\textbf{Open Source Contributions:} Active contributor to SZ compression library, CMake best practices, and scientific computing tools

\textbf{Professional Interests:} Cloud computing, DevOps, machine learning infrastructure, data engineering
}
\vspace{-4mm}

\end{document}
